---
title: "linear model from Web"
author: "Carmen Ramos-Caminos"
date: "July 14, 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS 

### scatterplot 
```{r}
plot(SIMS~ARM,data=data)
lmr =lm(SIMS~ARM,data=data)
abline (lmr)
```

The scatter plot for SIMS~ARMS shows a positive linear correlation.

### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```

The correlation is 0.6860 close to 0.07. 

### Inferential  (Build model.1)
```{r}
summary(lmr)
newdata=c(GRIP=94, ARM=88)
```

P-value 0.0000000000000002 and adjusted R-Sqaured is 0.467.

#### Predict at target point
```{r}
predictSIM = predict.lm(lmr, newdata=data.frame(GRIP = 94, ARM = 88))
print(predictSIM)
```

Predicted target point is postive 0.7.

#### scatterplot with model fit
```{r}
plot(lmr)
```
  
The standardized residuals graph shows a positive correlation. The remaining plot graphs run almost horizontal, but not a zero slope. 

## Model 2 SIM~GRIP 

### Now add in scatterplot
```{r}
plot(SIMS~ARM,data=data)
grip =lm(SIMS~ARM,data=data)
abline (grip)
```
  
The scatter plot for SIM~GRIP shows a positive linear correlation. 

### Numerical results 
```{r}
cor(SIMS~GRIP,data=data)
```

The correlation for SIMS~GRIP is 0.6398 slightly smaller than the correlation between SIMS~ARM. 

### Inferential  (Build model.2)
```{r}
summary(grip)
newdata=c(GRIP=94, ARM=88)
``` 
  
P-value 0.0000000000000002 and adjusted R-Sqaured is 0.467.

#### predict model.2 at target point
```{r}
predictSIM = predict.lm(grip, newdata=data.frame(GRIP = 94, ARM = 88))
print(predictSIM)
```
  
#### now add the model fit to our plot for model.2
```{r}
plot(grip)
```
  
The standardized residuals graph shows a positive correlation. The remaining plot graphs run almost horizontal, but not a zero slope. 


## Model 3 SIM~ARM+GRIP 

### Numerical results (cor)
```{r}
data2=lm(SIMS~ARM+GRIP, data+data)
summary(data2)
```
  
P-value 0.0000000000000002 and adjusted R-Sqaured is 0.5358

### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
```{r}
predict.lm(data2,newdat=data.frame(GRIP =94, ARM = 88))
print(predictSIM)
```
  
The prediction of the scatter plot is positive.

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
```{r}
anova(lmr,data2)
```

### Model.2 vs Model.3
```{r}
anova(grip,data2)
```
  
## Informally compare Model.1 with model.2





